---
title: "LR1"
author: "Riyaz Panjwani"
date: "September 27, 2016"
output: html_document
---

##Problem Statement 

##Grade Predictor using ML Algorithm 

A study was conducted in two well-known private institutes to determine the factors affecting
grades of students. The description of the attributes noted is as below :
Format:
<FeatureName ??? Description(<type>:<SetofPossibleValues>)>

To know more about :

##Approach to the problem 

The problem seems to be quite intuitive, using a regression algorithm is what comes to the mind. You could use Random Forest, Decision tree or any linear model. The data set is not very big with very less number of features. Before arriving to the conclusion of using the specified model and the obtaining the parameters for deciding the outcome a comprehensive study of data was performed using plotting and various visualization techniques (featurePlot, ggplot, plot etc.)

The final RMSE was found out to be 5.36, 6.39, 6.92 respectively for the predictions of G1, G2 and G3.

##Get Set Go 
##Getting the data 

In order to reproduce the same results, you need a certain set of packages, as well as setting a pseudo random seed equal to the one I used. Note:To install, for instance, the caret package in R, run this command: install.packages("caret")

The following Libraries were used for this project, which you should install - if not done yet - and load on your working environment

```{r}
library(lattice)
library(ggplot2)
library(caret)
library(car)
library(randomForest)
set.seed(1234)
```

For fast and accurate training the model, I choose lasso, Least absolute shrinkage and selection operator. Lasso is a penalized regression model. I have also tested the data with GBM, Gradient boosting model which led to almost the same error rate.

```{r}
train <- read.csv("G:\\training_set_q1.csv")
test <- read.csv("G:\\test_set_q1_upload.csv")

dim(train)
dim(test)
names(train)
```

##Clean Data 

The data appears to be clean with no **NA** values.The values are integers are the desired output is a value in the continuous range (0,20).

```{r}
trainG1 <- subset(train,select = -c(G2,G3))
trainG2 <- subset(train,select = -c(G1,G3))
trainG3 <- subset(train,select = -c(G1,G2))
```

##Data Slicing 

Slice the data for prediction and avoiding overfitting.

```{r}
inTrain <- createDataPartition(y = trainG1$G1,p=0.75,list = FALSE)
training <- trainG1[inTrain,]
testing <- trainG1[-inTrain,]
```

##Modal Fitting 

```{r}

#Modal Fit 
#modFit <- train(G1~.,methods = "gbm",data = training,verbose = FALSE)
modFitL1 <- train(G1~.,methods = "lasso",data = training,verbose = FALSE)
print(modFitL1)

```

##Plots 

Plot the prediction over the actual values.

```{r}

#Plots 
qplot(predict(modFitL1,testing),G1,data = testing)
```

##Prediction over testing set

```{r}
predL1 <- predict(modFitL1,testing)
rmse <- mean((testing$G1-predL1)^2)
print(rmse)
```

##Model fitting for G2

Using the same procedure for predicting the value of G2.

```{r}
inTrain <- createDataPartition(y = trainG2$G2,p=0.75,list = FALSE)
training <- trainG2[inTrain,]
testing <- trainG2[-inTrain,]

#modFitGBM2 <- train(G2~.,methods = "gbm",data = training,verbose = FALSE)
modFitL2 <- train(G2~.,methods = "lasso",data = training,verbose = FALSE)
print(modFitL2)

qplot(predict(modFitL2,testing),G2,data = testing)

#pred <- predict(modFit,testing)
predL2 <- predict(modFitL2,testing)
rmse <- mean((testing$G2-predL2)^2)
print(rmse)
```

##Modal fitting for G3

Using the same procedure for predicting the value of G3. 

```{r}
inTrain <- createDataPartition(y = trainG3$G3,p=0.75,list = FALSE)
training <- trainG3[inTrain,]
testing <- trainG3[-inTrain,]

modFitL3 <- train(G3~.,methods = "lasso",data = training,verbose = FALSE)
print(modFitL3)

qplot(predict(modFitL3,testing),G3,data = testing)

#pred      <- predict(modFit,testing)
predL3 <- predict(modFitL3,testing)
rmse <- mean((testing$G3-predL3)^2)
print(rmse)

```

##Final Submission 

This completes our analysis and it brings us to the final result which can be seen below

```{r}
##Predicting the test set

test.org <- read.csv("G:\\test_set_q1_upload.csv")
pred <- predict(modFitL1,test.org)
test$G1 <- pred
pred <- predict(modFitL2,test.org)
test$G2 <- pred
pred <- predict(modFitL3,test.org)
test$G3 <- pred
dim(test)
View(test)

```

